### 2016-04-20 msmfs.tex
Algorithm added, figures updated.

%%%% If you need a new symbol, please add it here. If really want to modify
%%%% one, do so, just take care to do a search-and-replace for the entire document
% Symbol definitions
\newcommand{\bytes}{b} % Length of a complex number in bytes
\newcommand{\cbytes}{b} % Length of a real number in bytes
\newcommand{\rbytes}{b} % Length of a complex number in bytes
\newcommand{\bl}{B} % Baseline length
\newcommand{\maxbl}{B_{\mathrm{max}}} % Maximum baseline length
\newcommand{\membw}{B_\mathrm{mem}} % Memory bandwidth
\newcommand{\pciebw}{B_\mathrm{PCIe}} % PCI-e bandwidth
\newcommand{\viscompr}{C} % Compression factor of visibilities for gridding
                          % for facets
\newcommand{\vism}{\mathbb{D}} % Matrix of observed visibilities
\newcommand{\da}{D_{\mathrm A}} % Extent of aperture
\newcommand{\ds}{D_{\mathrm s}} % Diameter of antennas/stations
\newcommand{\reff}{f_\mathrm{ref}} % Reference frequency
\newcommand{\fcc}{F_{\mathrm{cc}}} % Convolution kernel computational cost
\newcommand{\fci}{F_{\mathrm{ci}}} % Factor between bandwidth and FLOPS (bytes/ops)
\newcommand{\fgrid}{F_{\mathrm{grid}}} % Gridding cost
\newcommand{\fpatch}{f_\mathrm{patch}} % Fraction of the maximum baseline below which the uv coverage is almost filled
\newcommand{\fpr}{F_\mathrm{pr}} % Cost for phase rotation
\newcommand{\gainm}{\mathbb{G}} % 2x2 block diagonal matrix of complex gains
% To change to N_something
\newcommand{\modskyvism}{\mathbb{M}} % Matrix of model sky visibilities
\newcommand{\skymodbufsize}{M_\mathrm{buf,skymod}} % Size of the sky model buffer
\newcommand{\visbufsize}{M_\mathrm{buf,vis}} % Size of the visibility buffer
\newcommand{\visbufsizespec}{M^\mathrm{spec}_\mathrm{buf,vis}} % Size of the visibility buffer needed for spectral line processing
\newcommand{\visbufsizecont}{M^\mathrm{cont}_\mathrm{buf,vis}} % Size of the visibility buffer needed for continuum imaging
\newcommand{\bufsize}{M_\mathrm{cu,buf}} % Size of buffer
\newcommand{\slowmemsize}{M_\mathrm{cu,pool}} %	Size of slow working memory
\newcommand{\cumemsize}{M_\mathrm{cu,work}} % Size of working memory of compute unit
\newcommand{\imgsize}{M_\mathrm{image}} % Size of image (bytes)
\newcommand{\imgsizeoneax}{M_\mathrm{image,ax}}	% Image size along one axis
\newcommand{\nbyteperpix}{N_\mathrm{byte,pix}} % Number of bytes per pixel
%\newcommand{\nbytepervis}{N_\mathrm{byte,vis}} % Number of bytes per pixel
\newcommand{\targgridsize}{M_\mathrm{target}} %	Target grid size (per facet)
\newcommand{\uvgridsize}{M_{uv,\mathrm{grid}}} % Size of the uv-grid (bytes)
\newcommand{\vissize}{M_\mathrm{vis}} % Size of visibility data (bytes)
\newcommand{\wgridsize}{M_\mathrm{weight\_grid}} % Size of weight grid (bytes)
\newcommand{\gridcachesize}{M_{w,\mathrm{cache}}} % Cache size of
                                % gridding kernel
\newcommand{\ntel}{N_\mathrm{a}} % Number of antennas or stations in the array
\newcommand{\nateam}{N_\mathrm{A}} % Number of A-team sources
\newcommand{\ngridpakern}{N_\mathrm{AA}} % Number of grid points for A-kernel support (along one axis)
\newcommand{\naccvis}{N_\mathrm{apv}} % Number of accesses per visibility
\newcommand{\navg}{N_\mathrm{avg}} % Number of averages
\newcommand{\nbins}{N_\mathrm{bin}} % Number of bins
\newcommand{\nbeam}{N_\mathrm{beam}} % Number of beams simultaneously observed by the array
\newcommand{\rma}{N_{rma}} % Number of flops in real multiply and add
\newcommand{\cma}{N_{cma}} % Number of flops in complex multiply and add
\newcommand{\nbits}{N_\mathrm{bit}} %	Number of bits
\newcommand{\nbl}{N_\mathrm{bl}} % Number of baselines
\newcommand{\nbyteacc}{N_\mathrm{bpa}} % Number of bytes per access
\newcommand{\nbyte}{N_\mathrm{byte}} % Number of bytes
\newcommand{\nch}{N_\mathrm{ch}XXXWANT TO USE NF HERE} % Number of channels
\newcommand{\ncompu}{N_\mathrm{cu}} % Number of compute units
\newcommand{\ndatait}{N_\mathrm{datait}} % Number of data items required per source (e.g. postion)
\newcommand{\ngridp}{N_\mathrm{cvff}} % Number of grid points along one axis for the gridding convolution function
\newcommand{\nfch}{N_\mathrm{f}} % Number of frequency channels
\newcommand{\nfchcorr}{N_\mathrm{f,corr}} % Number of frequency channels output by the correlator
\newcommand{\nfnosmear}{N_\mathrm{f,smear}} % Number of frequency channels set by smearing limit
\newcommand{\nfchgrid}{N_\mathrm{f,grid}} % Number of frequency channels to be gridded
\newcommand{\nfchdegrid}{N_\mathrm{f,de-grid}} % Number of frequency channels to be de-gridded
\newcommand{\nfchout}{N_\mathrm{f,out}} % Number of output frequency channels
                                % (to be FFT-ed and reprojected or output from
                                % the CSP pulsar timing backend
\newcommand{\nfchdist}{N_\mathrm{f,distribute}} % Minimum number of frequencies needed to maintain distributability
\newcommand{\nfkernel}{N_\mathrm{f,kernel}} %Number of convolution kernels needed to cover frequency axis for a particular baseline
\newcommand{\nfacet}{N_\mathrm{facet}} % Number of facets along one axis
\newcommand{\facetoverlap}{r_\mathrm{facet}} %Facet overlap overhead
\newcommand{\nflop}{N_\mathrm{FLOP}} % Number of floating point operations
\newcommand{\nflopsamp}{N_\mathrm{FLOPsamp}} % Number of floating point
                                % operations per sample
\newcommand{\nflopvis}{N_\mathrm{FLOPvis}} % Number of floating point
                                % operations per visibility 
\newcommand{\npixgrid}{N_\mathrm{grid}} % Number of pixels in the grid (i.e. the square of the linear dimension)
\newcommand{\ngridwkern}{N_\mathrm{GW}} % Number of grid points for w-kernel
                                % support (along one axis)
\newcommand{\nit}{N_\mathrm{it}} % Number of iterations
\newcommand{\nawkern}{N_\mathrm{kernel}} % Linear size of combined A and w-kernels
\newcommand{\nmaj}{N_\mathrm{major}} % Number of major CLEAN cycles
\newcommand{\nmin}{N_\mathrm{minor}} % Number of minor CLEAN cycles
\newcommand{\nselfcal}{N_\mathrm{SelfCal}} %Number of self cal loops
% TODO: Factors should have another letter than N
\newcommand{\facgridoffdiagmuller}{N_\mathrm{mm}} % Factor to account for
                                % gridding of off-diagonal Mueller terms
% TODO: Factors should have another letter than N
\newcommand{\nops}{N_\mathrm{ops}} % Number of operations
\newcommand{\npatchpix}{N_\mathrm{patch,pix}} % Number of pixels of PSF to be used in minor cycle decorrelation
\newcommand{\npix}{N_\mathrm{pix}} % Number of pixels along one axis of a grid
\newcommand{\npixfacet}{N_\mathrm{pix,facet}} % Number of pixels along one axis of a single image facet
\newcommand{\npol}{N_\mathrm{pol}} % Number of polarisation products
\newcommand{\nsubint}{N_\mathrm{subint}} % Number of sub-integrations
\newcommand{\ntslot}{N_t} % Number of time slots
\newcommand{\ntaylor}{N_\mathrm{Tt}} % Number of Taylor terms
\newcommand{\ntslotave}{N_{t,\mathrm{av}}} % Number of time slots that are averaged (in de-mixing)
\newcommand{\nvis}{N_\mathrm{vis}} % Number of visibilities
\newcommand{\nvisrate}{R_{vis}} % Number of visibilities per second\\
% TODO: what kind of qfac?
\newcommand{\qfacbw}{Q_\mathrm{bw}} % Quality factor
\newcommand{\qfacreuse}{Q_\mathrm{fcv}} % Factor to allow for the reuse of functions between neighbouring frequency channels
\newcommand{\qfacfov}{Q_\mathrm{FoV}} % Quality factor defining how much bigger the diameter of the field of view is than the first zero of the Airy function
\newcommand{\facgridovers}{Q_\mathrm{GCF}} % Gridding oversampling factor
\newcommand{\facmsmf}{Q_\mathrm{MSMF}} % Factor to account for multiple subtractions (multi-frequency multi-scale CLEAN)
\newcommand{\qfacbeamovers}{Q_\mathrm{pix}} % Quality factor defining the
                                % oversampling of the synthesised beam
% TODO: what kind of qfac?
\newcommand{\qfac}{Q_t} % Quality factor
\newcommand{\corrfacw}{Q_w} % Correction factor for w values (0 to 1)
\newcommand{\earthrad}{R_\mathrm{Earth}} % Radius of the Earth ($6400\times 10^3$\,m)
\newcommand{\comprate}{R} % Compute rate (FLOPS)
\newcommand{\compratespec}{R^\mathrm{spec}} % Compute rate for spectral line processing
\newcommand{\compratecont}{R^\mathrm{cont}} % Compute rate for continuum imaging
\newcommand{\compratefast}{R^\mathrm{fast}} % Compute rate for fast imaging
\newcommand{\covm}{\mathbb{R}} % Covariance matrix
\newcommand{\covmfilt}{\mathbb{R}_\mathrm{filt}} % Filtered covariance matrix
\newcommand{\bwtoworkmem}{R_\mathrm{bw,mem}} % Bandwidth to working memory
\newcommand{\maxmembw}{R_\mathrm{bw,max}} % Maximum memory bandwidth of
                                % compute unit
\newcommand{\convkernflops}{R_\mathrm{CCF}} % Convolution kernel compute rate (FLOPS)
\newcommand{\fftflops}{R_\mathrm{FFT}} % FFT compute rate (FLOPS)
\newcommand{\flagflops}{R_\mathrm{flag}} % FLOP rate to do flagging on input visibilities
\newcommand{\griddingflops}{R_\mathrm{grid}} % Gridding compute rate (FLOPS)
\newcommand{\phaserotflops}{R_\mathrm{PR}} % Phase rotation compute rate (FLOPS)
\newcommand{\reprojflops}{R_\mathrm{RP}} % Re-projection compute rate (FLOPS)
\newcommand{\rcorr}{R_\mathrm{s}} % Correlator output rate (samples/sec)
\newcommand{\peakflop}{R_\mathrm{peak}} % Peak FLOPS of compute unit
% TODO - verschil met max mem bw of compute unit?
% TODO - verschil memory bw and bw to buffer?
\newcommand{\IO}{{R_\mathrm{IO}}} %IO rate
\newcommand{\maxiobwbuff}{R_\mathrm{bw,I/O,max}} % Maximum I/O bandwidth of compute unit to buffer
\newcommand{\bwbuff}{R_\mathrm{bw,I/O}} % Bandwidth to buffer
\newcommand{\bwbuffcont}{R^\mathrm{cont}_\mathrm{bw,I/O}} % Bandwidth to
                                % buffer for cotinuum imaging
\newcommand{\bwbuffspec}{R^\mathrm{spec}_\mathrm{bw,I/O}} % Bandwidth to
                                % buffer for spectral line processing
\newcommand{\nsource}{N_\mathrm{source}} % Number of sources
\newcommand{\telsensit}{S} % Telescope sensitivity
\newcommand{\corrdumpt}{t_\mathrm{dump}} % Correlator dump time (sec)
\newcommand{\compt}{t_{\mathrm{comp}}} % Computation time
\newcommand{\gridkernupdate}{t_\mathrm{kernel,update}} % Update timescale for gridding kernel
\newcommand{\lsmupdate}{t_\mathrm{LSM}} % Update timescale for the LSM
\newcommand{\obst}{t_{\mathrm{obs}}} % Observation time
\newcommand{\snapshot}{t_\mathrm{snap}} % Snapshot duration
\newcommand{\minsnapshot}{t_\mathrm{snap,min}} % Minimum duration of a snapshot in which w-correction is not dominated by Earth's curvature
\newcommand{\optsnapshot}{t_\mathrm{snap,opt}} % Optimum snapshot duration (sec)
\newcommand{\subint}{t_\mathrm{subint}} % Subintegration time
\newcommand{\uv}{uv} % Visibility coordinates
\newcommand{\uvw}{u,v,w} % Visibility coordinates
\newcommand{\w}{w} % Visibility w coordinate
\newcommand{\nbytepervis}{N_\mathrm{byte,vis}} %Memory per individual visibility 
\newcommand{\maxwdev}{\Delta w_\mathrm{max}} % Maximum deviation of the w
                                % coordinate due to the Earth's curvature
\newcommand{\minwdev}{\Delta w_\mathrm{min}} % Minimum deviation of the w
                                % coordinate due to the Earth's curvature
\newcommand{\spfiltm}{\mathbb{W}_\mathrm{filt}} % Spatial filter matrix
\newcommand{\fres}{\Delta f} % Frequency resolution
\newcommand{\tressmear}{t_\mathrm{smear}} % Smearing Time resolution (sec)
\newcommand{\tres}{t_{res}} % Time resolution (sec)
\newcommand{\fracconvfuncamp}{\epsilon_\omega} % Fraction of maximal amplitude of envelope of convolution function
\newcommand{\compeff}{\eta_\mathrm{comp}} % Computational efficiency
\newcommand{\fracfband}{\eta_f} % Fraction of frequency band
\newcommand{\beamsq}{\theta_\mathrm{bs}} % Beam squint
\newcommand{\fovdiam}{\theta_\mathrm{FoV}} % Angular diameter of the field of view (rad)
\newcommand{\pixres}{\theta_\mathrm{pix}} % Angular resolution of pixel size (rad)
\newcommand{\beamdiam}{\theta_\mathrm{PSF}} % Angular diameter of the synthesised beam (rad)
\newcommand{\wavel}{\lambda} % Wavelength
\newcommand{\maxwavel}{\lambda_\mathrm{max}} % Maximum wavelength
\newcommand{\minwavel}{\lambda_\mathrm{min}} % Minimum wavelength
\newcommand{\maxwavelsubb}{\lambda_{\mathrm{sub,max}}} % Maximum wavelength of an imaging sub-band (channels over which image and pixel size are matched)
\newcommand{\minwavelsubb}{\lambda_\mathrm{sub,min}} % Minimum wavelength of an imaging sub-band (channels over which image and pixel size are matched)
\newcommand{\earthrot}{\Omega_\mathrm{E}} % Angular velocity of the Earth (7.27 10-5 rad/sec)
\newcommand{\epsilonf}{\epsilon_f}  %Fraction of a uv cell that we allow uv track to move in time- or frequency- smearing-limited averaging
% Other command definitions
\newcommand{\Qkernel}{Q_\mathrm{kernel}} %Convolution kernel quality factor, for kernel re-use in frequency
\newcommand{\bs}{\texttt{\char`\\}}

@@

\newcommand{\dg}{^\dag}
\newcommand{\X}{\vec{x}}
\newcommand{\Xd}{\vec{{x}^\dag}}
\newcommand{\B}{\vec{b}}
\newcommand{\Bd}{\vec{b^\dag}}
\newcommand{\A}{{\tens{A}}}
\newcommand{\Ad}{{\tens{A^\dag}}}
\newcommand{\F}{{\tens{F}}}
\newcommand{\Fd}{{\tens{F^\dag}}}
\newcommand{\He}{{\tens{H}}}
\newcommand{\Sa}{{\tens{S}}}
\newcommand{\Sd}{{\tens{S^\dag}}}
\newcommand{\Sna}{\tens{{S_{\nu}}}}
\newcommand{\Snd}{\tens{{S_{\nu}^\dag}}}
\newcommand{\T}{{\tens{T}}}
\newcommand{\W}{{\tens{W}}}
\newcommand{\Wd}{{\tens{W^\dag}}}
\newcommand{\Pb}{{P_b}}

@@

% Add here the symbols used in your document
\clearpage \sdplistofsymbols
\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
\item[$\bytes$] Length of a complex number in bytes \vspace{-0.2cm}
\item[$\cbytes$] Length of a complex number in bytes \vspace{-0.2cm}
\item[$\rbytes$] Length of a real number in bytes \vspace{-0.2cm}
\item[$\bl$] Baseline length / GPU memory bandwidth \vspace{-0.2cm}
\item[$\maxbl$] Maximum baseline length \vspace{-0.2cm}
\item[$\membw$] Memory bandwidth \vspace{-0.2cm}
\item [$\pciebw$] PCI-e bandwidth \vspace{-0.2cm}
\item[$\viscompr$] Compression factor of visibilities for grdding for facets
  \textcolor{red}{This symbol is not used in the document, consider removing.}
  \vspace{-0.2cm}
\item[$\vism$] Matrix of observed visibilities \vspace{-0.2cm}
\item[$\da$] Extent of aperture \vspace{-0.2cm}
\item[$\ds$] Diameter of antennas/stations \vspace{-0.2cm}
\item[$\reff$] Reference frequency\vspace{-0.2cm}
\item[$\fcc$] Convolution kernel computational cost\vspace{-0.2cm}
\item[$\fci$] Factor between bandwidth and FLOPS (bytes/operations)\vspace{-0.2cm}
\item[$\fgrid$] Gridding cost\vspace{-0.2cm}
\item[$\fpatch$] Fraction of the maximum baseline below which the $\uv$
  coverage is almost filled\vspace{-0.2cm}
\item[$\fpr$] Cost for phase rotation\vspace{-0.2cm}
\item[$\gainm$] 2$\times$2 block diagonal matrix of complex
  gains\vspace{-0.2cm}
\item[$\modskyvism$] Matrix of model sky visibilities\vspace{-0.2cm}
\item[$\skymodbufsize$] Size of the sky model buffer\vspace{-0.2cm}
\item[$\visbufsize$] Size of the visibility buffer \vspace{-0.2cm}
\item[$\visbufsizespec$] Size of the visibility buffer needed for spectral line processing\vspace{-0.2cm}
\item[$\visbufsizecont$] Size of the visibility buffer needed for continuum imaging\vspace{-0.2cm}
\item[$\bufsize$] Size of buffer \vspace{-0.2cm}
\item[$\slowmemsize$] Size of slow working memory \vspace{-0.2cm}
\item[$\cumemsize$] Size of working memory of compute unit \vspace{-0.2cm}
\item[$\imgsize$] Size of image (bytes) \vspace{-0.2cm}
\item[$\imgsizeoneax$] Image size along one axis \vspace{-0.2cm}
\item[$\targgridsize$] Target grid size (per facet) \vspace{-0.2cm}
\item[$\uvgridsize$] Size of the $\uv$ grid (bytes) \vspace{-0.2cm}
\item[$\vissize$] Size of visibility data (bytes) \vspace{-0.2cm}
\item[$\wgridsize$] Size of weight grid (bytes)\vspace{-0.2cm}
\item[$\gridcachesize$] Cache size of gridding kernel \vspace{-0.2cm}
\item[$\nbins$] Number of bins \vspace{-0.2cm}
\item[$\ntel$] Number of antennas or stations in the array
  \vspace{-0.2cm}
\item[$\nateam$] Number of A-team sources \vspace{-0.2cm}
\item[$\ngridpakern$] Number of grid points for A-kernel support (along one
  axis) \vspace{-0.2cm}
\item[$\naccvis$] Number of accesses per visibility \vspace{-0.2cm}
\item[$\navg$] Number of averages\vspace{-0.2cm}
\item[$\nbeam$] Number of beams simultaneously observed by the array
  \vspace{-0.2cm}
\item[$\nbits$] Number of bits\vspace{-0.2cm}
\item[$\rma$] Number of flops in real multiply and add\vspace{-0.2cm}
\item[$\cma$] Number of flops in complex multiply and add\vspace{-0.2cm}
\item[$\nbl$] Number of baselines \vspace{-0.2cm}
\item[$\nbyteacc$] Number of bytes per access \vspace{-0.2cm}
\item[$\nbyte$] Number of bytes \vspace{-0.2cm}
\item[$\nbyteperpix$] Number of bytes per pixel \vspace{-0.2cm}
\item[$\nbytepervis$] Number of bytes per individual visibility

\item[$\nch$] Number of channels \vspace{-0.2cm}
\item[$\ncompu$] Number of compute units \vspace{-0.2cm}
\item[$\ndatait$] Number of data items required per source (e.g. position)\vspace{-0.2cm}
\item[$\ngridp$] Number of grid points along one axis for the gridding
  convolution function \vspace{-0.2cm}
\item[$\nfch$] Number of frequency channels/sub-bands \vspace{-0.2cm}
\item[$\nfchcorr$] Number of frequency channels output by the correlator
  \vspace{-0.2cm}
\item[$\nfchgrid$] Number of frequency channels to be gridded
  \vspace{-0.2cm}
\item[$\nfchdegrid$] Number of frequency channels to be de-gridded
  \vspace{-0.2cm}
\item[$\nfchout$] Number of frequency channels to be FFT-ed and reprojected
  (output) or output from the CSP pulsar timing backend\vspace{-0.2cm}
\item[$\nfchdist$] Minimum number of frequency channels to maintain distributability in the SDP
\item[$\nfkernel$] Number of convolution kernels needed to cover frequency axis for a given baseline
\item[$\nfacet$] Number of facets along one axis \vspace{-0.2cm}
\item[$\nflop$] Number of floating point operations
  \vspace{-0.2cm}
\item[$\nflopsamp$] Number of floating point operations per sample
  \vspace{-0.2cm}
\item[$\nflopvis$] Number of floating point operations per visibility
\item[$\npixgrid$] Number of pixels in the grid (i.e. the square of the linear
  dimension) \vspace{-0.2cm}
\item[$\ngridwkern$] Number of grid points for w-kernel support (along one
  axis) \vspace{-0.2cm}
\item[$\nit$] Number of iterations \vspace{-0.2cm}
\item[$\nawkern$] Linear size of combined A and $\w$-kernels \vspace{-0.2cm}
\item[$\nmaj$] Number of major CLEAN cycles (within each self-cal loop if appropriate) \vspace{-0.2cm}
\item[$\nselfcal$] Number of self-calibration cycles \vspace{-0.2cm}
\item[$\nmin$] Number of minor CLEAN cycles (within each major cycle loop if appropriate)\vspace{-0.2cm}
\item[$\facgridoffdiagmuller$] Factor to account for gridding of off-diagonal
  M\"uller terms \vspace{-0.2cm}
\item[$\nops$] Number of operations \vspace{-0.2cm}
\item[$\npatchpix$] Number of pixels of PSF to be used in minor cycle
  decorrelation \vspace{-0.2cm}
\item[$\npix$] Number of pixels along one axis of a grid\vspace{-0.2cm}
\item[$\npixfacet$] Number of pixels on one side of a facet \vspace{-0.2cm}
\item[$\npol$] Number of polarisation products \vspace{-0.2cm}
\item[$\nsource$] Number of sources \vspace{-0.2cm}
\item[$\ntslot$] Number of time slots \vspace{-0.2cm}
\item[$\ntaylor$] Number of Taylor terms (in MS-MFS)\vspace{-0.2cm}
\item[$\ntslotave$] Number of time slots that are averaged (in de-mixing)
  \vspace{-0.2cm}
\item[$\nvis$] Number of visibilities in an observation \vspace{-0.2cm}
\item[$\qfacbw$] Quality factor \vspace{-0.2cm}
\item[$\qfacreuse$] Factor to allow for the reuse of functions between
  neighbouring frequency channels \vspace{-0.2cm}
\item[$\qfacfov$] Quality factor defining how much bigger the diameter of the
  field of view is than the first zero of the Airy function \vspace{-0.2cm}
\item[$\facgridovers$] Gridding oversampling factor \vspace{-0.2cm}
\item[$\facmsmf$] Factor to account for multiple subtractions (multi-frequency
  multi-scale CLEAN\vspace{-0.2cm}
\item[$\qfacbeamovers$] Quality factor defining the oversampling of the
  synthesised beam \vspace{-0.2cm}
\item[$\qfac$] Quality factor \vspace{-0.2cm}
\item[$\Qkernel$] Convolution kernel quality factor, for kernel re-use in frequency
\item[$\corrfacw$] Correction factor for w values (0 to 1) \vspace{-0.2cm}
\item[$\earthrad$] Radius of the Earth ($6400\times 10^3$\,m) \vspace{-0.2cm}
\item[$\covm$] Covariance matrix \vspace{-0.2cm}
\item[$\covmfilt$] Filtered covariance matrix \vspace{-0.2cm}
\item[$\comprate$] Compute rate (FLOPS) \vspace{-0.2cm}
\item[$\compratespec$] Compute rate (FLOPS) for spectral line processing \vspace{-0.2cm}
\item[$\compratecont$] Compute rate (FLOPS) for continuum imaging \vspace{-0.2cm}
\item[$\compratefast$] Compute rate (FLOPS) for fast imaging \vspace{-0.2cm}
\item[$\bwtoworkmem$] Bandwidth to working memory \vspace{-0.2cm}
\item[$\maxmembw$] Maximum memory bandwidth of compute unit \vspace{-0.2cm}
\item[$\peakflop$] Peak FLOPS of compute unit \vspace{-0.2cm}

>>>>

%%%% If you need a new symbol, please add it here. If really want to modify
%%%% one, do so, just take care to do a search-and-replace for the entire document
% Symbol definitions

@@

\newcommand{\dg}{^\dag}
\newcommand{\X}{\vec{x}}
\newcommand{\Xd}{\vec{{x}^\dag}}
\newcommand{\B}{\vec{b}}
\newcommand{\Bd}{\vec{b^\dag}}
\newcommand{\A}{{\tens{A}}}
\newcommand{\Ad}{{\tens{A^\dag}}}
\newcommand{\F}{{\tens{F}}}
\newcommand{\Fd}{{\tens{F^\dag}}}
\newcommand{\He}{{\tens{H}}}
\newcommand{\Sa}{{\tens{S}{N}}}
\newcommand{\Sd}{{\tens{S^\dag}}}
\newcommand{\Sna}{\tens{{S_{\nu}}{N}}}
\newcommand{\Snd}{\tens{{S_{\nu}^\dag}}}
\newcommand{\T}{{\tens{T}}}
\newcommand{\W}{{\tens{W}}}
\newcommand{\Wd}{{\tens{W^\dag}}}
\newcommand{\Pb}{{P_b}}

@@

% Add here the symbols used in your document
%\clearpage \sdplistofsymbols
%\begin{basedescript}{\desclabelstyle{\pushlabel}\desclabelwidth{6em}}
%\item[$\bytes$] Length of a complex number in bytes \vspace{-0.2cm}
%\item[$\cbytes$] Length of a complex number in bytes \vspace{-0.2cm}
%\item[$\rbytes$] Length of a real number in bytes \vspace{-0.2cm}
%\item[$\bl$] Baseline length / GPU memory bandwidth \vspace{-0.2cm}
%\item[$\maxbl$] Maximum baseline length \vspace{-0.2cm}
%\item[$\membw$] Memory bandwidth \vspace{-0.2cm}
%\item [$\pciebw$] PCI-e bandwidth \vspace{-0.2cm}
%\item[$\viscompr$] Compression factor of visibilities for grdding for facets
%  \textcolor{red}{This symbol is not used in the document, consider removing.}
%  \vspace{-0.2cm}
%\item[$\vism$] Matrix of observed visibilities \vspace{-0.2cm}
%\item[$\da$] Extent of aperture \vspace{-0.2cm}
%\item[$\ds$] Diameter of antennas/stations \vspace{-0.2cm}
%\item[$\reff$] Reference frequency\vspace{-0.2cm}
%\item[$\fcc$] Convolution kernel computational cost\vspace{-0.2cm}
%\item[$\fci$] Factor between bandwidth and FLOPS (bytes/operations)\vspace{-0.2cm}
%\item[$\fgrid$] Gridding cost\vspace{-0.2cm}
%\item[$\fpatch$] Fraction of the maximum baseline below which the $\uv$
%  coverage is almost filled\vspace{-0.2cm}
%\item[$\fpr$] Cost for phase rotation\vspace{-0.2cm}
%\item[$\gainm$] 2$\times$2 block diagonal matrix of complex
%  gains\vspace{-0.2cm}
%\item[$\modskyvism$] Matrix of model sky visibilities\vspace{-0.2cm}
%\item[$\skymodbufsize$] Size of the sky model buffer\vspace{-0.2cm}
%\item[$\visbufsize$] Size of the visibility buffer \vspace{-0.2cm}
%\item[$\visbufsizespec$] Size of the visibility buffer needed for spectral line processing\vspace{-0.2cm}
%\item[$\visbufsizecont$] Size of the visibility buffer needed for continuum imaging\vspace{-0.2cm}
%\item[$\bufsize$] Size of buffer \vspace{-0.2cm}
%\item[$\slowmemsize$] Size of slow working memory \vspace{-0.2cm}
%\item[$\cumemsize$] Size of working memory of compute unit \vspace{-0.2cm}
%\item[$\imgsize$] Size of image (bytes) \vspace{-0.2cm}
%\item[$\imgsizeoneax$] Image size along one axis \vspace{-0.2cm}
%\item[$\targgridsize$] Target grid size (per facet) \vspace{-0.2cm}
%\item[$\uvgridsize$] Size of the $\uv$ grid (bytes) \vspace{-0.2cm}
%\item[$\vissize$] Size of visibility data (bytes) \vspace{-0.2cm}
%\item[$\wgridsize$] Size of weight grid (bytes)\vspace{-0.2cm}
%\item[$\gridcachesize$] Cache size of gridding kernel \vspace{-0.2cm}
%\item[$\nbins$] Number of bins \vspace{-0.2cm}
%\item[$\ntel$] Number of antennas or stations in the array
%  \vspace{-0.2cm}
%\item[$\nateam$] Number of A-team sources \vspace{-0.2cm}
%\item[$\ngridpakern$] Number of grid points for A-kernel support (along one
%  axis) \vspace{-0.2cm}
%\item[$\naccvis$] Number of accesses per visibility \vspace{-0.2cm}
%\item[$\navg$] Number of averages\vspace{-0.2cm}
%\item[$\nbeam$] Number of beams simultaneously observed by the array
%  \vspace{-0.2cm}
%\item[$\nbits$] Number of bits\vspace{-0.2cm}
%\item[$\rma$] Number of flops in real multiply and add\vspace{-0.2cm}
%\item[$\cma$] Number of flops in complex multiply and add\vspace{-0.2cm}
%\item[$\nbl$] Number of baselines \vspace{-0.2cm}
%\item[$\nbyteacc$] Number of bytes per access \vspace{-0.2cm}
%\item[$\nbyte$] Number of bytes \vspace{-0.2cm}
%\item[$\nbyteperpix$] Number of bytes per pixel \vspace{-0.2cm}
%\item[$\nbytepervis$] Number of bytes per individual visibility 
%
%\item[$\nch$] Number of channels \vspace{-0.2cm}
%\item[$\ncompu$] Number of compute units \vspace{-0.2cm}
%\item[$\ndatait$] Number of data items required per source (e.g. position)\vspace{-0.2cm}
%\item[$\ngridp$] Number of grid points along one axis for the gridding
%  convolution function \vspace{-0.2cm}
%\item[$\nfch$] Number of frequency channels/sub-bands \vspace{-0.2cm}
%\item[$\nfchcorr$] Number of frequency channels output by the correlator
%  \vspace{-0.2cm}
%\item[$\nfchgrid$] Number of frequency channels to be gridded
%  \vspace{-0.2cm}
%\item[$\nfchdegrid$] Number of frequency channels to be de-gridded
%  \vspace{-0.2cm}
%\item[$\nfchout$] Number of frequency channels to be FFT-ed and reprojected
%  (output) or output from the CSP pulsar timing backend\vspace{-0.2cm}
%\item[$\nfchdist$] Minimum number of frequency channels to maintain distributability in the SDP
%\item[$\nfkernel$] Number of convolution kernels needed to cover frequency axis for a given baseline
%\item[$\nfacet$] Number of facets along one axis \vspace{-0.2cm}
%\item[$\nflop$] Number of floating point operations
%  \vspace{-0.2cm}
%\item[$\nflopsamp$] Number of floating point operations per sample
%  \vspace{-0.2cm}
%\item[$\nflopvis$] Number of floating point operations per visibility
%\item[$\npixgrid$] Number of pixels in the grid (i.e. the square of the linear
%  dimension) \vspace{-0.2cm}
%\item[$\ngridwkern$] Number of grid points for w-kernel support (along one
%  axis) \vspace{-0.2cm}
%\item[$\nit$] Number of iterations \vspace{-0.2cm}
%\item[$\nawkern$] Linear size of combined A and $\w$-kernels \vspace{-0.2cm}
%\item[$\nmaj$] Number of major CLEAN cycles (within each self-cal loop if appropriate) \vspace{-0.2cm}
%\item[$\nselfcal$] Number of self-calibration cycles \vspace{-0.2cm}
%\item[$\nmin$] Number of minor CLEAN cycles (within each major cycle loop if appropriate)\vspace{-0.2cm}
%\item[$\facgridoffdiagmuller$] Factor to account for gridding of off-diagonal
%  M\"uller terms \vspace{-0.2cm}
%\item[$\nops$] Number of operations \vspace{-0.2cm}
%\item[$\npatchpix$] Number of pixels of PSF to be used in minor cycle
%  decorrelation \vspace{-0.2cm}
%\item[$\npix$] Number of pixels along one axis of a grid\vspace{-0.2cm}
%\item[$\npixfacet$] Number of pixels on one side of a facet \vspace{-0.2cm}
%\item[$\npol$] Number of polarisation products \vspace{-0.2cm}
%\item[$\nsource$] Number of sources \vspace{-0.2cm}
%\item[$\ntslot$] Number of time slots \vspace{-0.2cm}
%\item[$\ntaylor$] Number of Taylor terms (in MS-MFS)\vspace{-0.2cm}
%\item[$\ntslotave$] Number of time slots that are averaged (in de-mixing)
%  \vspace{-0.2cm}
%\item[$\nvis$] Number of visibilities in an observation \vspace{-0.2cm}
%\item[$\qfacbw$] Quality factor \vspace{-0.2cm}
%\item[$\qfacreuse$] Factor to allow for the reuse of functions between
%  neighbouring frequency channels \vspace{-0.2cm}
%\item[$\qfacfov$] Quality factor defining how much bigger the diameter of the
%  field of view is than the first zero of the Airy function \vspace{-0.2cm}
%\item[$\facgridovers$] Gridding oversampling factor \vspace{-0.2cm}
%\item[$\facmsmf$] Factor to account for multiple subtractions (multi-frequency
%  multi-scale CLEAN\vspace{-0.2cm}
%\item[$\qfacbeamovers$] Quality factor defining the oversampling of the
%  synthesised beam \vspace{-0.2cm}
%\item[$\qfac$] Quality factor \vspace{-0.2cm}
%\item[$\Qkernel$] Convolution kernel quality factor, for kernel re-use in frequency
%\item[$\corrfacw$] Correction factor for w values (0 to 1) \vspace{-0.2cm}
%\item[$\earthrad$] Radius of the Earth ($6400\times 10^3$\,m) \vspace{-0.2cm}
%\item[$\covm$] Covariance matrix \vspace{-0.2cm}
%\item[$\covmfilt$] Filtered covariance matrix \vspace{-0.2cm}
%\item[$\comprate$] Compute rate (FLOPS) \vspace{-0.2cm}
%\item[$\compratespec$] Compute rate (FLOPS) for spectral line processing \vspace{-0.2cm}
%\item[$\compratecont$] Compute rate (FLOPS) for continuum imaging \vspace{-0.2cm}
%\item[$\compratefast$] Compute rate (FLOPS) for fast imaging \vspace{-0.2cm}
